Supplementary material

### 2021-12-13 submission/manuscript.rmd
include discrimination and calibration plots to supplement

```{r adaptive, echo=FALSE, warning=FALSE, message=FALSE}
adaptiveSelections <- readr::read_csv(here::here("data/processed/adaptiveSelections.csv"))
rmseDistribution <- readr::read_csv(here::here("data/processed/rmseDistribution.csv"))
aucDistribution <- readr::read_csv(here::here("data/processed/discriminationDistribution.csv"))
```
The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = `r 4250` and AUC = 0.75), strong linear and even strong
quadratic deviations from a constant relative treatment effect
(Figure \ref{fig:rmsebase}; panels A-C). However, with
non-monotonic deviations from a constant relative treatment effect,
the RMSE of the linear interaction model increased substantially, 
especially in the presence of treatment-related harms (Figure 
\ref{fig:rmsebase}; panel D). In these scenarios, RCS-3 outperformed all other
methods in terms of RMSE. The constant treatment effect
approach had overall best performance under true constant treatment
effect settings, but was sensitive to all considered deviations,
resulting in increased RMSE. Finally, the adaptive approach had
comparable performance to the best-performing method in each
scenario. However, in comparison with the best-performing approach, its RMSE was
more variable across the 500 replications in the scenarios with linear and
non-monotonic deviations, especially when also including moderate or strong
treatment-related harms. This is caused by wrongly selecting the constant
treatment effect model in a substantial proportion of the replications
(Supplement, Figure S3).

In the scenario with a true constant relative treatment effects, the adaptive
approach selected the constant effect model for the majority of the replcations, even in
the presence of treatment-related harms
(`r adaptiveSelections %>% filter(scenarioId == 217) %>% pull(treatment) * 100`\%
of the replications without harms and 
`r adaptiveSelections %>% filter(scenarioId == 219) %>% pull(treatment) * 100`\% 
with strong harms). With strong linear or quadratic deviations and increasing
treatment-related harms the adaptive approach increasingly favored the linear
interaction model. With non-monotonic deviations, we observed increasing
selection frequencies for RCS-3 with increasing treatment harms (from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(rcs_3) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(rcs_3) * 100`\%
with strong harms), whereas selection frequencies for the linear interaction
model dropped from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(risk) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(risk) * 100`\%
with strong harms. Finally, in the case of strong linear and non-monotonic
deviations selection frequencies of the constant treatment effect model remained
high despite increasing treatment harms (Supplement, Table XX).

@@

Increasing the sample size to `r 17000` favored RCS-3 the most, as it
achieved lowest or close to lowest RMSE across all scenarios (Figure
\ref{fig:rmsesamplesize}). Especially in cases of strong quadratic and
non-monotonic deviations RCS-3 had lower RMSE (median 
`r rmseDistribution %>% filter(scenarioId == 385) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)`
for strong quadratic deviations and 
`r rmseDistribution %>% filter(scenarioId == 421) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)`
for non-monotonic deviations with no treatment-related harms) compared
to the linear interaction approach (median 
`r rmseDistribution %>% filter(scenarioId == 385) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)` and 
`r rmseDistribution %>% filter(scenarioId == 421) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)`,
respectively), regardless of the strength of treatment-related
harms. Due to the large sample size, the RMSE of the adaptive approach
was even more similar to the best-performing method, and the constant
relative treatment effect model was less often wrongly selected
(***numbers????***).

@@

When we increased the AUC of the true prediction model to 0.85 (OR =
0.8 and N = `r 4250`). RCS-3 had the lowest RMSE in the case of strong
quadratic or non-monotonic deviations and very comparable performance to
the -- optimal -- linear interaction model in the case of strong
linear deviations (median RMSE
`r rmseDistribution %>% filter(scenarioId == 297) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)` for RCS-3 compared to 
`r rmseDistribution %>% filter(scenarioId == 297) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)`
for the linear interaction model). As observed in the base case
scenario the adaptive approach wrongly selected the constant treatment
effect model
(`r adaptiveSelections %>% filter(scenarioId == 297) %>% pull(treatment) * 100`\%
and
`r adaptiveSelections %>% filter(scenarioId == 405) %>% pull(treatment) * 100`\%
of the replications in the strong linear and non-monotonic deviation
scenarios without treatment-related harms, respectively), leading to
more variability of the RMSE.

@@

```{r discrimination, cache=TRUE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 4,250.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_base.tiff")))
# knitr::include_graphics(here::here("figures/discrimination_base.png"))
```

@@

```{r calibration, cache=TRUE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 4,250.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

>>>>

```{r adaptive, echo=FALSE, warning=FALSE, message=FALSE}
adaptiveSelections <- readr::read_csv(here::here("data/processed/adaptiveSelections.csv"))
rmseDistribution <- readr::read_csv(here::here("data/processed/rmseDistribution.csv"))
aucDistribution <- readr::read_csv(here::here("data/processed/discriminationDistribution.csv"))
```

The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = `r 4250` and AUC = 0.75), strong linear and even strong
quadratic deviations from a constant relative treatment effect (Figure
\ref{fig:rmsebase}; panels A-C). However, with non-monotonic
deviations from a constant relative treatment effect, the RMSE of the
linear interaction model increased substantially, especially in the
presence of treatment-related harms (Figure \ref{fig:rmsebase}; panel
D). In these scenarios, RCS-3 outperformed all other methods in terms
of RMSE. The constant treatment effect approach had overall best
performance under true constant treatment effect settings, but was
sensitive to all considered deviations, resulting in increased
RMSE. Finally, the adaptive approach had comparable performance to the
best-performing method in each scenario. However, in comparison with
the best-performing approach, its RMSE was more variable across the
500 replications in the scenarios with linear and non-monotonic
deviations, especially when also including moderate or strong
treatment-related harms. This is caused by wrongly selecting the
constant treatment effect model in a substantial proportion of the
replications (Supplement, Figure S1).

@@

Increasing the sample size to `r 17000` favored RCS-3 the most, as it
achieved lowest or close to lowest RMSE across all scenarios (Figure
\ref{fig:rmsesamplesize}). Especially in cases of strong quadratic and
non-monotonic deviations RCS-3 had lower RMSE (median 
`r rmseDistribution %>% filter(scenarioId == 385) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)`
for strong quadratic deviations and 
`r rmseDistribution %>% filter(scenarioId == 421) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)`
for non-monotonic deviations with no treatment-related harms) compared
to the linear interaction approach (median 
`r rmseDistribution %>% filter(scenarioId == 385) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)` and 
`r rmseDistribution %>% filter(scenarioId == 421) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)`,
respectively), regardless of the strength of treatment-related
harms. Due to the large sample size, the RMSE of the adaptive approach
was even more similar to the best-performing method, and the constant
relative treatment effect model was less often wrongly selected
(Supplement, Figure S2).

@@

When we increased the AUC of the true prediction model to 0.85 (OR =
0.8 and N = `r 4250`). RCS-3 had the lowest RMSE in the case of strong
quadratic or non-monotonic deviations and very comparable performance to
the -- optimal -- linear interaction model in the case of strong
linear deviations (median RMSE
`r rmseDistribution %>% filter(scenarioId == 297) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_rcs_3)` for RCS-3 compared to 
`r rmseDistribution %>% filter(scenarioId == 297) %>% mutate(across(-one_of("scenarioId"), ~ d(.x, decimals = 3))) %>% pull(median_linear)`
for the linear interaction model). As observed in the base case
scenario the adaptive approach wrongly selected the constant treatment
effect model
(`r adaptiveSelections %>% filter(scenarioId == 297) %>% pull(treatment) * 100`\%
and
`r adaptiveSelections %>% filter(scenarioId == 405) %>% pull(treatment) * 100`\%
of the replications in the strong linear and non-monotonic deviation
scenarios without treatment-related harms, respectively), leading to
more variability of the RMSE (Supplement, Figure S3).

@@

```{r discrimination, cache=TRUE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 4,250.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_base.tiff")))
# knitr::include_graphics(here::here("figures/discrimination_base.png"))
```

@@

```{r calibration, cache=TRUE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 4,250.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

### 2021-12-13 submission/manuscript.tex
include discrimination and calibration plots to supplement

The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = 4,250 and AUC = 0.75), strong linear and even strong quadratic
deviations from a constant relative treatment effect (Figure
\ref{fig:rmsebase}; panels A-C). However, with non-monotonic deviations
from a constant relative treatment effect, the RMSE of the linear
interaction model increased substantially, especially in the presence of
treatment-related harms (Figure \ref{fig:rmsebase}; panel D). In these
scenarios, RCS-3 outperformed all other methods in terms of RMSE. The
constant treatment effect approach had overall best performance under
true constant treatment effect settings, but was sensitive to all
considered deviations, resulting in increased RMSE. Finally, the
adaptive approach had comparable performance to the best-performing
method in each scenario. However, in comparison with the best-performing
approach, its RMSE was more variable across the 1000 replications in the
scenarios with linear and non-monotonic deviations, especially when also
including moderate or strong treatment-related harms. This is caused by
wrongly selecting the constant treatment effect model in a substantial
proportion of the replications (Supplement, Table XX).

In the scenario with a true constant relative treatment effects, the
adaptive approach selected the constant effect model for the majority of
the replcations, even in the presence of treatment-related harms (96\%
of the replications without harms and 88\% with strong harms). With
strong linear or quadratic deviations and increasing treatment-related
harms the adaptive approach increasingly favored the linear interaction
model. With non-monotonic deviations, we observed increasing selection
frequencies for RCS-3 with increasing treatment harms (from 32\% with no
harms to 53\% with strong harms), whereas selection frequencies for the
linear interaction model dropped from 40\% with no harms to 7\% with
strong harms. Finally, in the case of strong linear and non-monotonic
deviations selection frequencies of the constant treatment effect model
remained high despite increasing treatment harms (Supplement, Table XX).

@@

Increasing the sample size to 17,000 favored RCS-3 the most, as it
achieved lowest or close to lowest RMSE across all scenarios (Figure
\ref{fig:rmsesamplesize}). Especially in cases of strong quadratic and
non-monotonic deviations RCS-3 had lower RMSE (median 0.011 for strong
quadratic deviations and 0.010 for non-monotonic deviations with no
treatment-related harms) compared to the linear interaction approach
(median 0.013 and 0.014, respectively), regardless of the strength of
treatment-related harms. Due to the large sample size, the RMSE of the
adaptive approach was even more similar to the best-performing method,
and the constant relative treatment effect model was less often wrongly
selected (\textbf{\emph{numbers????}}).

@@

When we increased the AUC of the true prediction model to 0.85 (OR = 0.8
and N = 4,250). RCS-3 had the lowest RMSE in the case of strong
quadratic or non-monotonic deviations and very comparable performance to
the -- optimal -- linear interaction model in the case of strong linear
deviations (median RMSE 0.016 for RCS-3 compared to 0.014 for the linear
interaction model). As observed in the base case scenario the adaptive
approach wrongly selected the constant treatment effect model (23\% and
25\% of the replications in the strong linear and non-monotonic
deviation scenarios without treatment-related harms, respectively),
leading to more variability of the RMSE.

>>>>

The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = 4,250 and AUC = 0.75), strong linear and even strong quadratic
deviations from a constant relative treatment effect (Figure
\ref{fig:rmsebase}; panels A-C). However, with non-monotonic deviations
from a constant relative treatment effect, the RMSE of the linear
interaction model increased substantially, especially in the presence of
treatment-related harms (Figure \ref{fig:rmsebase}; panel D). In these
scenarios, RCS-3 outperformed all other methods in terms of RMSE. The
constant treatment effect approach had overall best performance under
true constant treatment effect settings, but was sensitive to all
considered deviations, resulting in increased RMSE. Finally, the
adaptive approach had comparable performance to the best-performing
method in each scenario. However, in comparison with the best-performing
approach, its RMSE was more variable across the 500 replications in the
scenarios with linear and non-monotonic deviations, especially when also
including moderate or strong treatment-related harms. This is caused by
wrongly selecting the constant treatment effect model in a substantial
proportion of the replications (Supplement, Figure S1).

@@

Increasing the sample size to 17,000 favored RCS-3 the most, as it
achieved lowest or close to lowest RMSE across all scenarios (Figure
\ref{fig:rmsesamplesize}). Especially in cases of strong quadratic and
non-monotonic deviations RCS-3 had lower RMSE (median 0.011 for strong
quadratic deviations and 0.010 for non-monotonic deviations with no
treatment-related harms) compared to the linear interaction approach
(median 0.013 and 0.014, respectively), regardless of the strength of
treatment-related harms. Due to the large sample size, the RMSE of the
adaptive approach was even more similar to the best-performing method,
and the constant relative treatment effect model was less often wrongly
selected (Supplement, Figure S2).

@@

When we increased the AUC of the true prediction model to 0.85 (OR = 0.8
and N = 4,250). RCS-3 had the lowest RMSE in the case of strong
quadratic or non-monotonic deviations and very comparable performance to
the -- optimal -- linear interaction model in the case of strong linear
deviations (median RMSE 0.016 for RCS-3 compared to 0.014 for the linear
interaction model). As observed in the base case scenario the adaptive
approach wrongly selected the constant treatment effect model (23\% and
25\% of the replications in the strong linear and non-monotonic
deviation scenarios without treatment-related harms, respectively),
leading to more variability of the RMSE (Supplement, Figure S3).

### 2021-12-13 submission/supplement.rmd
include discrimination and calibration plots to supplement

```{r adaptiveBase, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for the base case scenario true prediction AUC of 0.75, sample size of 4250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveSampleSize, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for sample size of 17000.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveAuc, cache=TRUE, echo=FALSE, fig.cap="Adaptive model selection rates for true prediction AUC of 0.85.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

```{r rmseHighBase, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect base", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighSampleSize, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect sample size", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighAuc, cache=TRUE, echo=FALSE, fig.cap="RMSE high effect auc", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

>>>>

```{r adaptiveBase, cache=TRUE, echo=FALSE, fig.cap="Model selection frequencies of the adaptive approach based on Akaike's Information Criterion across 500 replications. The scenario with the true constant relative treatment effect (first panel) had a true prediction AUC of 0.75 and sample size of 4,250. ", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveSampleSize, cache=TRUE, echo=FALSE, fig.cap="Model selection frequencies of the adaptive approach based on Akaike's Information Criterion across 500 replications. Sample size is 17,000 rather than 4,250 in Figure \\ref{fig:adaptiveBase}", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r adaptiveAuc, cache=TRUE, echo=FALSE, fig.cap="Model selection frequencies of the adaptive approach based on Akaike's Information Criterion across 500 replications. AUC is 0.85 rather than 0.75 in Figure \\ref{fig:adaptiveBase}", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

# Discrimination and calibration for benefit

```{r discriminationSampleSize, cache=FALSE, echo=FALSE, fig.cap="Sample size", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r discriminationAuc, cache=FALSE, echo=FALSE, fig.cap="Auc", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationSampleSize, cache=FALSE, echo=FALSE, fig.cap="Calibration Sample size", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationAuc, cache=FALSE, echo=FALSE, fig.cap="Calibration Auc", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

```{r rmseHighBase, cache=TRUE, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replications calculated in a simulated super-population of size 500,000. The scenario with true constant relative treatment effect (panel A) had a true prediction AUC of 0.75 and sample size of 4,250. The RMSE is also presented for strong linear (panel B), strong quadratic (panel C), and non-monotonic (panel D) deviations from constant relative treatment effects. Panels on the right side present the true relationship between baseline risk (x-axis) and absolute treatment benefit (y-axis). The 2.5, 25, 75 and 97.5 percentiles of the risk distribution are expressed in the boxplot.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighSampleSize, cache=TRUE, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replcations calculated in a simulated sample of size 500,000. Sample size is 17,000 rather than 4,250 in Figure \\ref{fig:rmseHighBase}.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseHighAuc, cache=TRUE, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replcations calculated in a simulated sample of size 500,000. AUC is 0.85 rather than in Figure \\ref{fig:rmseHighBase}.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
